---
title: "mbruner3_8"
author: "Mark Bruner"
date: "10/19/2020"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
```{r}
rm(list=ls())
```

```{r}
library(Benchmarking)
library(lpSolveAPI)
library(ucminf)
library(tidyverse)
library(gt)
```
# HOPE VALLEY HEALTH CARE ASSOC.

#### DEA Formulation
**Our DMU's are the 6 different nursing home facilities. The inputs are staffing labor (measured in average hours per day) and the cost of supplies (in
thousands of dollars per day). The outputs are the number of patient-days reimbursed by third-party sources and the number of patient-days reimbursed privately.**

# QUESTIONS 1 & 2: Formulate and Model Analysis
#### Summary of Performance Data
```{r}
y <- as.data.frame(matrix(c(14000, 3500, 14000, 21000, 42000, 10500, 28000, 42000, 19000, 25000, 14000, 15000), ncol = 2, byrow = TRUE))
x <- as.data.frame(matrix(c(150, .2, 400, .7, 320, 1.2, 520, 2.0, 350, 1.2, 320, .7),ncol = 2, byrow = TRUE))

hope_valley <- cbind(x, y)
rownames(hope_valley) <- c("F1","F2","F3","F4","F5","F6")
colnames(hope_valley) <- c("reimbur_patient_day", "priv_patient_day", "st_hour_day","supplies_day")

str(hope_valley) 
```
#### FDH Model
```{r}
fdh <- dea(x, y, RTS = "fdh")            # provide the input and output 

as.data.frame(peers(fdh)) -> p_fdh                       # identify the peers
p_fdh %>% 
  rename(fdhP1 = peer1) -> p_fdh

as.data.frame(lambda(fdh)) -> l_fdh                    # identify the relative weights given to the peers
l_fdh %>% 
  rename(fdhL1 = L1, fdhL2 = L2, fdhL3 = L3, fdhL4 = L4, fdhL5 = L5, fdhL6 = L6) -> l_fdh

p_fdh
```

```{r}
l_fdh
```

```{r}
e_fdh <- fdh$eff
```

The results indicate that DMUs 1 through 6 are all efficient. Their peers are themselves.

**Note: I did have the plots included for each model but because there exists two inputs and two outputs, I found the plots unhelpful since they would be more than two dimensional.**

#### VRS Model
```{r}
vrs <- dea(x, y, RTS = "vrs")            # provide the input and output 

as.data.frame(peers(vrs)) -> p_vrs                       # identify the peers
p_vrs %>% 
  rename(vrsP1 = peer1, vrsP2 = peer2, vrsP3 = peer3) -> p_vrs

as.data.frame(lambda(vrs)) -> l_vrs                    # identify the relative weights given to the peers
l_vrs %>% 
  rename(vrsL1 = L1, vrsL2 = L2, vrsL3 = L3, vrsL4 = L4, vrsL5 = L5) -> l_vrs
p_vrs
```

```{r}
l_vrs
```

```{r}
e_vrs <- vrs$eff
```

The results indicate that DMUs 1 through 5 are efficient. DMU(6) is only 89.63% efficient. Further, the peer units for DMU(6) are 1, 2, and 5, with relative weights 0.401, .342 and 0.256. 

#### DRS Model
```{r}
drs <- dea(x, y, RTS = "drs")            # provide the input and output 

as.data.frame(peers(drs)) -> p_drs                       # identify the peers
p_drs %>% 
  rename(drsP1 = peer1, drsP2 = peer2, drsP3 = peer3) -> p_drs

as.data.frame(lambda(drs)) -> l_drs                    # identify the relative weights given to the peers
l_drs %>% 
  rename(drsL1 = L1, drsL2 = L2, drsL3 = L3, drsL4 = L4) -> l_drs
p_drs
```

```{r}
l_drs
```

```{r}
e_drs <- drs$eff
```

The results indicate that DMUs 1 through 4 are efficient. DMU(5) is only 97.75% efficient, and DMU(6) is 86.75% efficient. For DMU(5), the peer units are 1, 2, and 4, with relative weights 0.200, .080 and 0.538. For DMU(6), the peer units are 1, 2, and 4, with relative weights 0.343, .395 and 0.131.  

#### CRS model
```{r}
crs <- dea(x,y,RTS = "crs")            # provide the input and output 

as.data.frame(peers(crs)) -> p_crs                       # identify the peers
p_crs %>% 
  rename(crsP1 = peer1, crsP2 = peer2, crsP3 = peer3) -> p_crs

as.data.frame(lambda(crs)) -> l_crs                    # identify the relative weights given to the peers
l_crs %>% 
  rename(crsL1 = L1, crsL2 = L2, crsL3 = L3, crsL4 = L4) -> l_crs
p_crs
```

```{r}
l_crs
```

```{r}
e_crs <- crs$eff
```

The results indicate that DMUs 1 through 4 are efficient. DMU(5) is only 97.75% efficient, and DMU(6) is 86.75% efficient. Further, the peer units for DMU(5) are 1, 2, and 4, with relative weights 0.200, .080 and 0.538. Similarly for DMU(6), the peer units are 1, 2, and 4, with weights 0.342, .395, and 0.131, respectively. **Same result as the CRS model.**

#### IRS model
```{r}
irs <- dea(x,y,RTS = "irs")            # provide the input and output 

as.data.frame(peers(irs)) -> p_irs                       # identify the peers
p_irs %>% 
  rename(irsP1 = peer1, irsP2 = peer2, irsP3 = peer3) -> p_irs

as.data.frame(lambda(irs)) -> l_irs                    # identify the relative weights given to the peers
l_irs %>% 
  rename(irsL1 = L1, irsL2 = L2, irsL3 = L3, irsL4 = L4, irsL5 = L5) -> l_irs

p_irs
```

```{r}
l_irs
```

```{r}
e_irs <- irs$eff
```

The results indicate that DMUs 1 through 5 are efficient. DMU(6) is only 89.63% efficient. Further, the peer units for DMU(6) are 1, 2, and 5, with relative weights 0.401, .342 and 0.256.

#### FRH model
```{r}
frh <- dea(x,y,RTS = "add")            # provide the input and output 

as.data.frame(peers(frh)) -> p_frh                       # identify the peers
p_frh %>% 
  rename(frhP1 = peer1) -> p_frh

as.data.frame(lambda(frh)) -> l_frh                    # identify the relative weights given to the peers
l_frh %>% 
  rename(frhL1 = L1, frhL2 = L2, frhL3 = L3, frhL4 = L4, frhL5 = L5, frhL6 = L6) -> l_frh

p_frh
```

```{r}
l_frh
```

```{r}
e_frh <- frh$eff
```

The results indicate that DMUs 1 through 6 are all efficient. Their peers are themselves.

# QUESTION 3: Summary of Results

#### Hope Valley Facility Efficiencies 
```{r}
hope_valley_eff <- as.data.frame(cbind(c(1:6),e_crs, e_drs, e_fdh, e_frh, e_irs, e_vrs))
gt(
  data = hope_valley_eff
) %>%
  tab_header(
    title = "Hope Valley Facility Efficiencies"
) %>% 
  cols_label(
    V1 = "DMU",
    e_crs = "CRS Eff",
    e_drs = "DRS Eff",
    e_fdh = "FDH Eff",
    e_frh = "FRH Eff",
    e_irs = "IRS Eff",
    e_vrs = "VRS Eff"
) %>% 
  fmt_number (
    vars(e_crs, e_drs, e_fdh, e_frh, e_irs, e_vrs),
    decimals = 2
) %>% 
  opt_table_lines(
) %>%
  data_color(
    columns = vars(e_crs, e_drs, e_fdh, e_frh, e_irs, e_vrs),
    colors = c("red", "orange", "green")
)
```

#### Hope Valley Facility Peers 
```{r}
hope_valley_peers <- as.data.frame(cbind(p_crs, p_drs, p_fdh, p_frh, p_irs, p_vrs))

gt(
  data = hope_valley_peers
) %>%
  tab_header(
    title = "Hope Valley Facility Peers"
) %>% 
  tab_spanner(
    label = "CRS",
    vars(crsP1, crsP2, crsP3)
) %>% 
  tab_spanner(
    label = "DRS",
    vars(drsP1, drsP2, drsP3)
) %>% 
  tab_spanner(
    label = "FDH",
    vars(fdhP1)
) %>%  
  tab_spanner(
    label = "FRH",
    vars(frhP1) 
) %>% 
    tab_spanner(
    label = "IRS",
    vars(irsP1, irsP2, irsP3)
) %>% 
  tab_spanner(
    label = "VRS",
    vars(vrsP1, vrsP2, vrsP3)
) %>%
  data_color(
    columns = vars(vrsP1, vrsP2, vrsP3, irsP1, irsP2, irsP3, frhP1, fdhP1, drsP1, drsP2, drsP3, crsP1, crsP2, crsP3),
    colors = c("red", "orange", "green")
) 
```

#### Hope Valley Facility Lambda
```{r}
hope_valley_lamb <- cbind(l_crs, l_drs, l_fdh, l_frh, l_irs, l_vrs)

gt(
  data = hope_valley_lamb
) %>%
  tab_header(
    title = "Hope Valley Facility Lambda"
) %>% 
  tab_spanner(
    label = "CRS",
    vars(crsL1, crsL2, crsL3, crsL4)
) %>% 
  tab_spanner(
    label = "DRS",
    vars(drsL1, drsL2, drsL3, drsL4)
) %>% 
  tab_spanner(
    label = "FDH",
    vars(fdhL1, fdhL2, fdhL3, fdhL4, fdhL5, fdhL6)
) %>%  
  tab_spanner(
    label = "FRH",
    vars(frhL1, frhL2, frhL3, frhL4, frhL5, frhL6) 
) %>% 
    tab_spanner(
    label = "IRS",
    vars(irsL1, irsL2, irsL3, irsL4, irsL5)
) %>% 
  tab_spanner(
    label = "VRS",
    vars(vrsL1, vrsL1, vrsL3, vrsL4, vrsL5)
) %>% 
  fmt_number (
    vars(crsL1, crsL2, crsL3, crsL4, drsL1, drsL2, drsL3, drsL4, fdhL1, fdhL2, fdhL3, fdhL4, fdhL5, fdhL6, frhL1, frhL2, frhL3, frhL4, frhL5, frhL6, irsL1, irsL2, irsL3, irsL4, irsL5, vrsL1, vrsL2, vrsL3, vrsL4, vrsL5),
    decimals = 2
)%>%
  data_color(
    columns = vars(crsL1, crsL2, crsL3, crsL4, drsL1, drsL2, drsL3, drsL4, fdhL1, fdhL2, fdhL3, fdhL4, fdhL5, fdhL6, frhL1, frhL2, frhL3, frhL4, frhL5, frhL6, irsL1, irsL2, irsL3, irsL4, irsL5, vrsL1, vrsL2, vrsL3, vrsL4, vrsL5),
    colors = c("red", "orange", "green")
)
```

# QUESTION 4
#### **Compare/Contrast**
All six models agree that DMU's 1 to 4 are efficient/frontiers. DMU 5 and 6 are the facilities where they differ in results. DMU(6) has similar efficiency of 4 out of the 6 models. This tells me that the performance at this facility can be improved using the peers suggested. Two of the models include DMU(5) as a frontier, while the other two have DMU(5) as inefficient. This seems to me to be that situation where a business has to decide how conservative they want their model to be and what assumptions they are good with assuming. I would say though that DMU's 1 to 4 are the most efficient facilities in Hope Valley. 
