---
title: "Assignment 11"
author: "Mark Bruner"
date: "11/17/2020"
output:
  pdf_document: default
  html_document: default
---

```{r}
rm(list=ls())
```

```{r}
library(lpSolveAPI)
library(kableExtra)
```

```{r}
ip <- read.lp("worker.lp")
ip
```

```{r}
solve(ip)
get.objective(ip)
get.variables(ip)
```

## SUMMARY OF RESULTS

### **Objective Function Minimization**
* The lowest weekly employee cost is **$25,675.** 

### **Employees Working Each Shift Per Day**

#### **Table 1:**
 
```{r}
Shift <- c(1:7)
Employees <- c(2, 4, 5, 0, 8, 1, 13)
table1 <- cbind(Shift, Employees)

table1 %>% 
         kbl(caption = "Most Employees Work Shifts 5 and 7") %>% 
        kable_classic(full_width = FALSE) %>% 
        kable_styling(bootstrap_options = "striped", position = "center") %>% 
       column_spec(1, bold = TRUE) %>% 
        row_spec(1, color = "white", background = "#41B3A3") %>%
        row_spec(2, color = "white", background = "#41B3A3") %>% 
        row_spec(3, color = "white", background = "#41B3A3") %>% 
        row_spec(4, color = "white", background = "#41B3A3") %>% 
        row_spec(5, bold = T, background = "#C38D9E") %>% 
        row_spec(6, color = "white", background = "#41B3A3") %>% 
        row_spec(7, bold = T, background = "#C38D9E") %>% 
        row_spec(0, bold = T) 
```
 
 **Explanation:** Shift 7 has the highest number of employees working due to it being the lowest cost of weekly wage of $750. Shift 5 has a higher amount due to needing to make sure the weekend employee constraint was met for Saturday.
 
### **Total Employees Working Per Day**
#### **Table 2:**
 
```{r}
Days <- c("Sun", "Mon", "Tues", "Wed", "Thurs", "Fri", "Sat")
Tot_Employees <- c(18, 27, 24, 28, 25, 24, 19)
table2 <- cbind(Days, Tot_Employees)

table2 %>% 
        kbl(caption = "Most Employees Are Working on Week Days") %>% 
        kable_classic(full_width = FALSE) %>% 
        kable_styling(bootstrap_options = "striped", position = "center") %>% 
       column_spec(1, bold = TRUE) %>% 
        row_spec(1, color = "white", background = "#B22222") %>%
        row_spec(2:6, background = "#97CAEF") %>% 
        row_spec(7, color = "white", background = "#B22222") %>% 
        row_spec(0, bold = T)
```

 
 **Explanation:** The algorithm met exactly the constraints for Sat. and Sun. to minimize costs on the more expensive days for the company. 
 