---
title: "mbruner3.6"
author: "Mark Bruner"
date: "9/30/2020"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(lpSolveAPI)
```
# Defining decision variables and objective function
```{r}
lprec <- make.lp(0, 6)
lp.control(lprec, sense = "min")
set.objfn(lprec, c(622, 614, 630, 641, 645, 649))
```
# set constraints
Capacity Constraints
```{r}
add.constraint(lprec, c(rep(1, 3)), indices = c(1, 2, 3), "<=", 100)
add.constraint(lprec, c(rep(1, 3)), indices = c(4, 5, 6), "<=", 120)
add.constraint(lprec, c(rep(1, 2)), indices = c(1, 4), "=", 80)
add.constraint(lprec, c(rep(1, 2)), indices = c(2, 5), "=", 60)
add.constraint(lprec, c(rep(1, 2)), indices = c(3, 6), "=", 70)

set.bounds(lprec, lower = c(0, 0, 0, 0, 0, 0))
```

# Decision Variable Names
```{r}
RowNames <- c("A", "B", "W1", "W2", "W3")
ColNames <- c("A1","A2","A3", "B1","B2","B3")

dimnames(lprec) <- list(RowNames, ColNames)
lprec
```

```{r}
library(dplyr)
write.lp(lprec, filename = "lprec.lp")
x <- read.lp(filename = "lprec.lp")

solve(x)
get.objective(x)
get.constraints(x)     # get constraint RHS values
get.variables(x)
```
# Summary of results

The minimum cost of producing and delivering the AED to each of the warehouse is $132,790.

To achieve the minimum cost, Plant A & B should produce 100 and 110 AED's respectively in order to maximize the demand for each warehouse (80, 60, 70 units respectively for Warehouses 1 to 3). Plant A should deliver 60 AED's to Warehouse 2. Plant A should deliver 40 AED's to Warehouse 3. Plant B should deliver 80 AED's to Warehouse 1. Plant B should deliver 30 AED's to Warehouse 3. 