---
title: "mbruner3_mod4"
author: "Mark Bruner"
date: "9/21/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lpSolveAPI)
```
# Defining decision variables and objective function
```{r}
factory <- make.lp(0, 9)
lp.control(factory, sense = "max")
set.objfn(factory, c(420, 360, 300, 420, 360, 300, 420, 360, 300))
```
# set constraints
Capacity Constraints
```{r}
add.constraint(factory, c(rep(1, 3)), indices = c(1, 2, 3), "<=", 750)
add.constraint(factory, c(rep(1, 3)), indices = c(4, 5, 6), "<=", 900)
add.constraint(factory, c(rep(1, 3)), indices = c(7, 8, 9), "<=", 450)
```

Square Footage
```{r}
add.constraint(factory, c(20, 15,12), indices = c(1, 2, 3), "<=", 13000)
add.constraint(factory, c(20, 15, 12), indices = c(4, 5, 6), "<=", 12000)
add.constraint(factory, c(20, 15, 12), indices = c(7, 8, 9), "<=", 5000)
```

Sales
```{r}
add.constraint(factory, c(rep(1, 3)), indices = c(1, 4, 7), "<=", 900)
add.constraint(factory, c(rep(1, 3)), indices = c(2, 5, 8), "<=", 1200)
add.constraint(factory, c(rep(1, 3)), indices = c(3, 6, 9), "<=", 750)
```

Same percentage of capacity
```{r}
add.constraint(factory, c(rep(900, 3), rep(-750, 3)), indices = c(1, 2, 3, 4, 5, 6), "=", 0)
add.constraint(factory, c(rep(450, 3), rep(-750, 3)), indices = c(1, 2, 3, 7, 8, 9), "=", 0)

set.bounds(factory, lower = c(rep(0, 9)), columns = c(1:9))
```

# Decision Variable Names
```{r}
RowNames <- c("Capacity 1", "Capacity 2", "Capacity 3", "Sqft1", "Sqft2", "Sqft3", "Sales 1", "Sales 2", "Sales 3", "Same 1", "Same 2")
ColNames <- c("L1","M1","S1", "L2", "M2", "S2", "L3", "M3", "S3")
dimnames(factory) <- list(RowNames, ColNames)
dimnames(factory)
```

# Solve LP model
```{r}
solve(factory)
```
Optimize Objective Function
```{r}
get.objective(factory)
```

Decision Variables
```{r}
get.variables(factory)
```


# Interpreting the output from optimization routines

In order to satisfy the constraints on the LP Model, the Weigelt Corporation should produce the following quantities of L, M, and S at each factory:

Factory 1 (space = 13000 sq ft and capacity is 750 units.)
L1 = 516.6667 
M1 = 177.7778   
S1 = 0.00000

Factory 2 (space = 12000 sq ft and capacity is 900 units.)
L2 =  0.00000 
M2 = 666.6667 
S2 = 166.6667

Factory 3 (space = 5000 sq ft and capacity is 450 units.)
L3 = 0
M3 = 0
S3 = 416.6667

# Interpreting optimal objective function value:
If the above production occurs at each factory, optimal amount of money they can expect in profit per day.
~$696,000




