---
title: "mbruner3_mod4"
author: "Mark Bruner"
date: "9/21/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lpSolveAPI)
```
# defining decision variables and objective function
```{r}
factory <- make.lp(9, 9)
lp.control(factory, sense = "max")
set.objfn(factory, c(420, 420, 420, 360, 360, 360, 300, 300, 300))
```
# set constraints
```{r}
add.constraint(factory, c(20, 0, 0, 15, 0, 0, 12, 0, 0), "<=", 13000)
add.constraint(factory, c(0, 20, 0, 0, 15, 0, 0, 12, 0), "<=", 12000)
add.constraint(factory, c(0, 0, 20, 0, 0, 15, 0, 0, 12), "<=", 5000)
add.constraint(factory, c(1, 1, 1), indices = c(1, 4, 7), "<=", 750)
add.constraint(factory, c(1, 1, 1), indices = c(2, 5, 8), "<=", 900)
add.constraint(factory, c(1, 1, 1), indices = c(3, 6, 9), "<=", 450)
add.constraint(factory, c(1, 1, 1), indices = c(1, 4, 7), "<=", 900)
add.constraint(factory, c(1, 1, 1), indices = c(2, 5, 8), "<=", 1200)
add.constraint(factory, c(1, 1, 1), indices = c(3, 6, 9), "<=", 750)
add.constraint(factory, c(1/750, 1/750, 1/750, -1/900, -1/900, -1/900), indices = c(1, 2, 4, 5, 7, 8), "=", 0)
add.constraint(factory, c(1/750, 1/750, 1/750, -1/900, -1/900, -1/900), indices = c(1, 3, 4, 6, 7, 9), "=", 0)
```
# Solve LP model
```{r}
solve(factory)
get.objective(factory)
get.variables(factory)
```
# Interpreting the output from optimization routines
L1 = 481.81818
L2 = 203.48837
L3 = 0.00000
M1 = 48.48485
M2 = 0.00000
M3 = 0.00000
S1 = 219.69697
S2 = 660.85271
S3 = 416.66667

In order to satisfy the constraints on the LP Model, the Weigelt Corporation should produce the following quantities of L, M, and S at each factory:

Factory 1 (space = 13000 sq ft and capacity is 750 units.)
L1 = 481.81818
M1 = 48.48485
S1 = 220.69697

Factory 2 (space = 12000 sq ft and capacity is 900 units.)
L2 = 203.48837
M2 = 0
S2 = 660.85271

Factory 3 (space = 5000 sq ft and capacity is 450 units.)
L3 = 0
M3 = 0
S3 = 416.66667

# Interpreting optimal objective function value:
If the above production occurs at each factory, optimal amount of money they can expect in profit per day.
~$694,448.20




